---
title: "Preliminary analysis of KorNLI dataset"
format: html
editor: visual
---

## Dataset

KorNLI, a Korean natural language inference (NLI) dataset, is derived from the Stanford NLI (SNLI), MultiGenre NLI (MNLI), and Cross-lingual NLI (XNLI) datasets.

The dataset consists of pairs of sentences–a premise `sentence1` and a hypothesis `sentence2`–and a label for the relation between them as one of entailment, contradiction, or neutral.

#### About the dataset

The training data from these English datasets were machine translated, as well as XNLI's development and test data. The BERT-translated evaluation set (development and test data) were then manually edited and proofread by professional translators.

Training data consists of 942,854 examples. Evaluation data consists of 7,500 examples.

For more information, refer to its [paper](https://arxiv.org/pdf/2004.03289), "KorNLI and KorSTS: New Benchmark Datasets for Korean Natural Language Understanding."

## Loading and cleaning the data

```{r}
library(conflicted)
library(tidyverse)
```

```{r}
dev_url <- 'https://raw.githubusercontent.com/kakaobrain/kor-nlu-datasets/refs/heads/master/KorNLI/xnli.dev.ko.tsv'
nli_dev <- read_tsv(dev_url, col_names = TRUE)
```

```{r}
problems(nli_dev)
```

```{r}
test_url <- 'https://raw.githubusercontent.com/kakaobrain/kor-nlu-datasets/refs/heads/master/KorNLI/xnli.test.ko.tsv'
nli_test <- read_tsv(test_url, col_names = TRUE)
```

```{r}
problems(nli_test)
```

```{r}
nli_dev_clean <- nli_dev %>% drop_na()
nli_test_clean <- nli_test %>% drop_na()
```

```{r}
eval_df <- rbind(nli_dev_clean, nli_test_clean)
```

## Preliminary analysis

This preliminary analysis looks at number of occurrences of *amwu*, Korean 'any' in the evaluation set.

```{r}
amwu_eval_df <- eval_df %>%
  dplyr::filter(grepl("아무", sentence1) | grepl("아무", sentence2))
```

```{r nominal-bar-label}
amwu_eval_df %>%
  ggplot(aes(x = gold_label)) +
  geom_bar() +
  labs(x = "Label", y = "Count") +
  scale_y_continuous(labels = scales::comma) +
  theme_classic()
```
